\documentclass[letterpaper]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage[sfdefault]{biolinum}
\usepackage[x11names]{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{layout}
\usepackage{tikz}
\usetikzlibrary{shadows.blur}

\usepackage[unicode=true]{hyperref}

\definecolor{primary}{HTML}{277ed1}
\newcommand{\primary}{\color{primary}}

\definecolor{primarylight}{HTML}{e4f3fd}
\newcommand{\primarylight}{\color{primarylight}}

\definecolor{primarydark}{HTML}{1650a0}
\newcommand{\primarydark}{\color{primarydark}}

\definecolor{complementary}{HTML}{dca021}
\newcommand{\complementary}{\color{complementary}}

\definecolor{complementarylight}{HTML}{ffc529}
\newcommand{\complementarylight}{\color{complementarylight}}

\definecolor{complementaryscant}{HTML}{ffe194}
\newcommand{\complementaryscant}{\color{complementaryscant}}

\hypersetup{
  pdfborder={0 0 0},
  colorlinks=true,
  urlcolor=primarydark,
  breaklinks=true,
}
\urlstyle{same}  % don't use monospace font for urls

\newcommand{\mapMarker}{\faMapMarker*[alt]}

\newcommand{\headerItem}[3]{\href{#1}{#3 \hspace{-2pt} #2}}

\newcommand{\email}
{\headerItem{mailto:michaelstergianis@gmail.com}{michael.stergianis@gmail.com}{\faEnvelope}}

\newcommand{\github}
{\headerItem{https://github.com/mstergianis}{github.com/mstergianis}{\faGithub}}

\newcommand{\phone}{\headerItem{tel:+1-905-626-2050}{(905)-626-2050}{\faPhone}}

\newcommand{\portfolio}{\headerItem{https://michael.stergianis.ca}{Portfolio}{\faBriefcase{}}}

\newcommand{\location}
{\headerItem{https://en.wikipedia.org/wiki/Oshawa}{Oshawa, ON}{\mapMarker} }

\newenvironment{heading}[1]{%
  {\LARGE \primarydark \textbf{#1}}\\ {\complementary
    \rule[5pt]{\linewidth}{0.6pt}}
}
{\par\vspace{8pt}}

\newcommand{\blockend}{\vspace{4pt}}

\newenvironment{experience}[4]{
  { #1 \par}
  {\small \primary #2 \par}
  \begin{tabularx}{\linewidth}{ l l }
    { \small \faCalendar \space #3 } & { \small \mapMarker \space #4 }
  \end{tabularx}%
}{
  \blockend{}
}

\newenvironment{project}[2]{%
  { #1 \par }
  { \small \primary #2 \par }%
}{
  \blockend{}
}

\newenvironment{itemize*}%
{\begin{itemize}[topsep=0pt,leftmargin=20pt]%
    \setlength{\itemsep}{0pt}%
    \setlength{\parsep}{0pt}%
    \setlength{\parskip}{0pt}%
    \small%
  }%
  {\end{itemize}}

\newenvironment{prose}{\small}{\par}

\newcommand{\skill}[1]{%
  \begin{tikzpicture}%
    \node[anchor=base,
          fill=primarylight,
          draw=complementaryscant,
          inner xsep=0ex,
          inner ysep=.5ex,
          thick,
          minimum height=5mm,
          rounded corners=0.8mm]%
    {\begin{tabular}{c} {\small #1} \end{tabular}};%
  \end{tikzpicture}%
}

\newcommand{\hobby}[2]{%
  {\small {\primarydark{#1}} #2} \par \vspace{2pt}
}

\setlength{\parindent}{0pt}

\pagestyle{empty}

\begin{document}
{\huge \textbf{Michael Stergianis}}\\
{\large \primary \textbf{Programmer}}
\\

\begingroup
\hypersetup{
  urlcolor=.,
}
\begin{tabularx}{\linewidth}{ l l l l l }
  \phone & \email & \github & \portfolio{} & \location \\
\end{tabularx}\\
\endgroup

\begin{minipage}[t]{0.59\textwidth}%
  \begin{heading}{Attributes}
    \begin{itemize*}
    \item Eager to take on a leadership role.
    \item Willing to give an opinion without being strongly attached.
    \item Helps peers through problems.
    \item Quickly picks up concepts from others.
    \item Able to effectively explain complex concepts.
    \item Investigates problems deeply until they have an answer.
    \item Able to work independently or in a group.
    \end{itemize*}
  \end{heading}
  %
  \begin{heading}{Experience}%
    \begin{experience}{Senior Software Engineer}
      {VMware -- Broadcom Inc. (by acquisition)}
      {Jan 2022 -- Oct 2024}
      {(Remote) Oshawa, Ontario}
      Served as technical lead on the Tanzu Developer Portal team.
      \begin{itemize*}
      \item Was central to the product's successful release during multiple
        release deadlines.
      \item Worked with key stakeholders to interpret customer needs and scope
        new tracks.
      \item Started a series of meetings where engineers would come together to
        talk about technical debt; the meeting produced actionable items in the
        backlog.
      \item Performed and taught others to do CVE triaging.
      \item Worked one on one with users to understand their pain and determine
        solutions.
      \end{itemize*}
    \end{experience}
    %
    \begin{experience}{Software Engineer 3}
      {VMware}
      {Oct 2020 -- Jan 2022}
      {(Remote) Oshawa, Ontario}
      Continued to hone my skills.
      \begin{itemize*}
      \item Joined a new team and was invited to participate in planning
        meetings. Allowing me to help steer the technical and product outcomes
        of the project.
      \item Performed a
        \href{https://github.com/vmware-archive/octant/pull/2581}{large
          refactor} on an unfamiliar codebase to a custom transport mechanism to
        be used in our proprietary product.
      \end{itemize*}
    \end{experience}

    \begin{experience}{Software Engineer 2}
      {Pivotal -- VMware (by acquisition)}
      {Aug 2019 -- Oct 2020}
      {Toronto, Ontario -- (Remote) Oshawa, Ontario}
      Joined a full-stack team and began my journey.
      \begin{itemize*}
      \item Led and designed a track of work where a complex software system,
        \href{https://github.com/vmware-tanzu-labs/cf-mgmt}{cf-mgmt}, was
        automated using \href{https://github.com/libgit2/git2go}{git2go}.
        \item Performed medium size refactor in the front-end to reuse code.
        \item Maintained a full stack codebase in Golang and Typescript.
        \item Learned pair programming and Test Driven Development (TDD).
        \item Became the team anchor (technical lead).
      \end{itemize*}
    \end{experience}

    \begin{heading}{Education}
      \begin{experience}{HBSc. Computer Science}
        {University of Ontario Institute of Technology}
        {Sep 2014 -- Apr 2018}
        {Oshawa, Ontario}
        \begin{itemize*}
          \item Graduated with Highest Distinction.
          \item Maintained the highest GPA among peers.
        \end{itemize*}
      \end{experience}
    \end{heading}
  \end{heading}

\end{minipage}%
\hspace{0.02\textwidth}%
\begin{minipage}[t]{0.39\textwidth}%
  \begin{heading}{Skills}
    \begingroup
    \hypersetup{urlcolor=.}
    \href{https://www.typescriptlang.org/}{\skill{Typescript}}
    \href{https://react.dev/}{\skill{React}}
    \href{https://go.dev/}{\skill{Golang}}
    \href{https://en.wikipedia.org/wiki/Test-driven_development}{\skill{TDD}}
    \href{https://fluxcd.io/}{\skill{FluxCD}}
    \href{https://kubernetes.io/}{\skill{Kubernetes}}
    \href{https://en.wikipedia.org/wiki/Bash_(Unix_shell)}{\skill{Bash}}
    \href{https://www.linux.org/}{\skill{Linux}}
    \href{https://www.vim.org/}{\skill{Vim}}
    \endgroup
  \end{heading}

  \begin{heading}{Projects}
    \begin{project}{Homelab}{Maintains a home server infrastructure.}%
      \begin{itemize*}
      \item NAS running \href{https://www.truenas.com/}{TrueNAS} with a ZFS RAID
        array.
      \item Multi-node kubeadm deployed
        \href{https://kubernetes.io/}{kubernetes} cluster.
      \item NFS storage class for apps that need persistent disc.
      \item Kubernetes manifests managed in git using FluxCD.
      \end{itemize*}
    \end{project}

    \begin{project}{Tanzu Developer Portal}
      {Maintained a codebase split across several teams and repositories}%
      \begin{itemize*}
      \item Full stack web app in Node and React that enabled users to create
        internal developer portals.
      \item Several teams, approximately 30 engineers total, maintained plugins
        that were reviewed and integrated by our team.
      \item Was the first Backstage offering to market with \linebreak no-code
        configurable plugins.
      \item Featured a \href{https://carvel.dev}{carvel} install that automated
        away many pain points of the Backstage install process.
      \end{itemize*}
    \end{project}

    \begin{project}{Ship of Harkinian}
      {A PC port of The Legend of Zelda: Ocarina of Time}%
      \begin{prose}
        My friend and I added a text filter to the
        \href{https://www.shipofharkinian.com/}{Ship of Harkinian} randomizer
        check tracker. For more information, check out the
        \href{https://michael.stergianis.ca/posts/adding-a-text-filter-to-the-ship-of-harkinian-randomizer-check-tracker/}{blog
          post} I wrote on this.
      \end{prose}
    \end{project}
    %
  \end{heading}
  %
  \begin{heading}{Hobbies}
    \hobby{Cooking}{means so much to me. As a way of communicating love, a form
      of self care, meditation, and of course the results are delicious.}

    \hobby{Crosswords}{are my recreational puzzle of choice. My current best NYT
      Monday time is 4:34.}

    \hobby{Bouldering}{allows me to push my body to its limits while working
      through complex spatial problems.}

    \hobby{Hiking}{in nature is one of my favourite ways to spend my time.
      Sometimes I work out complex problems in my head, or simply clear it.}
  \end{heading}
\end{minipage}
\end{document}
